\chapter{Related Work}
\label{chap:related_work}

In this chapter we go over some of the other work that has been done in the field.

\section{Conventional Quality Assessment}

Researchers used a convolutional neural network to assess the quality of documents \cite{ocr_cnn_docu_2014}.
The documents were segmented into text and non-text regions.
Then \gls{ocr} and the proposed \gls{cnn} were used to predict scores, which were analyzed for correlation.
The \gls{cnn} achieved state of the art performance in assessing the quality of the documents.
However, the authors noted that one assumption was, that the \gls{ocr} performance is directly correlated with the quality of the degraded document.
Due to the similarity of text regions in documents and screen content, we might be able to verify or disprove this assumption in this thesis.

\section{Screen Content Specific Quality Assessment}

In \cite{text_pict_weight_2017} the authors propose a objective metric that considers the text and pictorial content of an image separately.
Afterwards, the two scores are weighted and combined.

The paper \cite{3_subj_weight_2015} uses a subjective score, that is split and considers text, pictorial and the entire image separately.
The correlation between the three scores is then analyzed, weighted and used to combine them into a single score.

- No reference vs full reference, we have full reference
- most papers use ocr as a comparison, almost like ground truth, or predict when ocr is good


\section{Optical Character Recognition}

\cite{ocr_survey_2017}

\subsection{Conventional Optical Character Recognition}

\subsection{Deep Learning Optical Character Recognition}

- is there natural language processing involved? might improve results, even if visual quality is low
- connection threshold of boundingbox, difficult to set correctly, cant use dict if single letters, auto puts sentences together when high
- qualtiy assesment for machines, not humans, useful too, blind person on zoom, computer needs to read

\subsection{EasyOCR}
\label{subsec:easyocr}

EasyOCR is a Python library for \gls{ocr} \cite{easyocr_2020}. It uses a deep learning model to detect text.

\subsection{Tesseract}
\label{subsec:tesseract}

Tesseract is an \gls{ocr} engine \cite{tesseract_2007}. It is open-source and was developed by Google. It is written in C++ and has a Python wrapper.

\subsection{Other Optical Character Recognition Methods}
\label{subsec:other_ocr_methods}

We don't use other \gls{ocr} methods in this thesis.
However, we mention them here for completeness.

sections:

- related work:
    - put ocr (tess, ezocr) in
- codecs to dataset (creating new dataset)

- Metrics of Comparison

% ## Text Recognition Algorithms

% ### Tesseract

% https://github.com/tesseract-ocr/tesseract

% paper: https://ieeexplore.ieee.org/document/4376991
% but author only author until 2018

% settings: https://tesseract-ocr.github.io/tessdoc/ImproveQuality.html

% ### Paddle OCR

% https://github.com/PaddlePaddle/PaddleOCR
% paper: https://arxiv.org/abs/2009.09941
% python quickstart: https://github.com/PaddlePaddle/PaddleOCR/blob/release/2.6/doc/doc_en/quickstart_en.md
% model summary: https://github.com/PaddlePaddle/PaddleOCR/blob/release/2.6/doc/doc_en/algorithm_overview_en.md
% not sure yet how to use specific models

% ### Ocropus

% https://github.com/ocropus/ocropy
% no paper
% seems to be experimental, not as stable

% ### Kraken OCR

% https://github.com/mittagessen/kraken
% paper: https://arxiv.org/ftp/arxiv/papers/1703/1703.09550.pdf

% ### Microsoft OCR

% https://learn.microsoft.com/en-us/azure/cognitive-services/computer-vision/quickstarts-sdk/client-library?tabs=visual-studio&pivots=programming-language-python

% ### MMOCR

% https://github.com/open-mmlab/mmocr

% ### Vedastr
% https://github.com/Media-Smart/vedastr
% small? but simple library

% ## Models

% Maybe look for stuff here: https://huggingface.co/models?sort=downloads&search=ocr

% ### Mask OCR
% https://paperswithcode.com/paper/maskocr-text-recognition-with-masked-encoder


% ## Fitting/Methods

% - https://www.researchgate.net/profile/Guangtao-Zhai/publication/341011181_Perceptual_image_quality_assessment_a_survey/links/61812d24a767a03c14e3d754/Perceptual-image-quality-assessment-a-survey.pdf
%     - Survey on perceptual image quality assessment
%     - suggests different fitting model

% - https://vqeg.org/VQEGSharedFiles/Publications/Validation_Tests/FRTV_Phase2/FRTV_Phase2_Final_Report.pdf
%     - VQEG Final Report
%     - suggests 3 parameter fitting model and dmos_p


% ## Other Literature

% - https://paddleocr.bj.bcebos.com/ebook/Dive_into_OCR.pdf
%     - OCR book

% - https://engineering.fb.com/2018/09/11/ai-research/rosetta-understanding-text-in-images-and-videos-with-machine-learning/
%     - Facebook paper on text recognition
%     - rosetta

% - https://research.aimultiple.com/ocr-technology/
%     - current state of OCR

% - https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=156468
%     - Historical Review of OCR Research and Development 
%     - way too old, 1992

% - https://projet.liris.cnrs.fr/imagine/pub/proceedings/ICPR-2012/media/files/0043.pdf
%     - Method to estimate sharpness in images with natural and text images

% - https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9151144
%     - Handwritten Optical Character Recognition (OCR): A Comprehensive Systematic Literature Review (SLR)
%     - handwritten, but maybe still interesting, as there aren't many algorithms that are trained on screen content

% - https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=9183326
%     - Text extraction using OCR: A Systematic Review
%     - might be a good overview

% - http://39.96.165.147/Pub%20Files/2017/fym_tip17.pdf
%     - Fusing of text and pictoral regions
%     - uses similar fitting and metrics

% - http://sim.jxufe.cn/JDMKL/pdf/Perceptual%20quality%20assessment%20of%20screen%20content%20images.pdf
%     - Metric that considers 3 subjective scores and weight them

% - https://scholarsmine.mst.edu/cgi/viewcontent.cgi?article=5864&context=ele_comeng_facwork
%     - Predicting user perception, can be used to predict ocr performance

% - https://arxiv.org/pdf/1807.04047.pdf
%     - ocr as ground truth

% - https://dl.acm.org/doi/pdf/10.1145/3606692
%     - document image quality assesment survey
